Balsa: A Compact Line Notation Based on SMILES

### 2022-07-01 manuscript.tex
Adds figure for PPB errors states. Closes #10.
Adds figure for PPB error state exceptions. Closes #11.
Adds figure for bridged PPB. Closes #12

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Error bond states. Because conformational descriptions are defined over three or more bonds, a variety of error states are possible.}
    \label{fig:bond-error-states}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Error state exceptions. Conjugated dienes sharing a common PPB can lead to exceptional cases.}
    \label{fig:bond-error-state-exceptions}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Bridged PPB Bond. A bridge across a PPB yields two bonds of opposite direction.}
    \label{fig:bridged-ppb-bond}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{ppb-error-states.pdf}
    \caption{PPB error states. Because conformational descriptions are defined over three or more bonds, a variety of error states are possible.}
    \label{fig:bond-error-states}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{ppb-error-state-exception.pdf}
    \caption{Error state exceptions. Conjugated dienes sharing a common PPB can lead to exceptional cases. The direction of the rightmost bond does not need to be set.}
    \label{fig:bond-error-state-exceptions}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{bridged-ppb-bond.pdf}
    \caption{Bridged PPB Bond. A bridge across a PPB yields two bonds of opposite direction (right).}
    \label{fig:bridged-ppb-bond}
\end{figure}
